---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# blair

<!-- badges: start -->
<!-- badges: end -->

This is my personal package to organize functions I often find myself going back and copy pasting so that 1) I amd using the same versions across projects and 2) reproducibility. 

## Installation

You can install the development version of blair from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sophiebmoore00/blair")
```

## Example

For example, I save color palettes I like to `palettes()`, and the available palette names can be found with `get_palettes()`

```{r example}
library(blair)

get_palettes()

palettes("blues")
palettes("one")
```

And the palettes can be used to easily color plots: 

```{r}
library(ggplot2)
ggplot(mtcars, aes(x = wt, y = mpg, color = as.factor(gear))) +
  geom_point() +
  scale_color_manual(values = palettes("one"))
```

